### 2021-02-24 main.tex
Version shared with collaborators

	\begin{theorem}
		Let $X$ be locally compact and Hausdorff and $Y \subseteq X$ (compact? check where used).
		\begin{itemize}
			\item[$(r^n)$] If $K$ and $M$ are compact subsets of $X$ with $\widetilde K = K \cap Y \subset \interior M$, then $\im r^n_{\widetilde K, M}$ is finite.
			\item[$(r^n_\bullet)$] If $V$ is a neighborhood in $X$ of $y \in Y$ there exist another such neighborhood $U \subseteq V$ such that $\im r^n_{U \cap Y, V}$ is finite.
		\end{itemize}
		Then, ($r^{n-1}$) together with ($r^n_\bullet$) imply ($r^n$).
	\end{theorem}

	\begin{proof}
		Let $M$ be fixed and let $\sigma$ be the set of compact subsets $K$ of $\interior M$ such that $K$ has a neighborhood $U_K$ such that $\im r^n_{U_K \cap Y, M}$ is finite.

		Notice that $\sigma$ contains a compact neighborhood of each $y \in Y$ because of $(r^n_\bullet)$. This because locally compact together with Hausdorff imply that for any element $y$ and open $U_y$ there exist $K_y$ compact with $y \in K_y \subseteq U_y$.

		Let $K_1, K_2 \in \sigma$ and let $K_i^\prime$ be a compact neighborhood of $K_i$ such that $\im r^n_{K^\prime_i \cap Y, M}$ is finite. Such $K^\prime_i$ since (fill details using compactness of $K_i$ and the above property of locally compact Hausdorff spaces).

		Let $K_i^{\dprime}$ be a compact neighborhood of $K_i$ with $K_i^{\dprime} \subseteq \interior K_i^\prime$. (Fill in the details again.)

		Use $\widetilde{K}$ to denote $K \cap Y$ we have the commutative diagram
		\begin{equation*}
		\begin{tikzcd}
		& \arrow[r] \arrow[d] H^n(M) & H^n(M) \oplus H^n(M) \arrow[d] \\
		H^{n-1}(\widetilde K_1^\prime \cap \widetilde K_2^\prime) \arrow[r] \arrow[d] & 
		H^{n}(\widetilde K_1^\prime \cup \widetilde K_2^\prime) \arrow[r] \arrow[d] &
		H^{n}(\widetilde K_1^\prime) \oplus H^n(\widetilde K_2^\prime) \\
		H^{n-1}(\widetilde K_1^\dprime \cap \widetilde K_2^\dprime) \arrow[r] & 
		H^{n}(\widetilde K_1^\dprime \cup \widetilde K_2^\dprime). &
		\end{tikzcd}
		\end{equation*}
		The upper right square has a finite image because $\im r^n_{\widetilde K^\prime_i, M}$ is. The bottom left square has a finite image using property $(r^n)$ with $K = K_1^\dprime \cap K_2^\dprime$ and $M = \widetilde K_1^\prime \cap \widetilde K_2^\prime$. And checking that $\interior(K_i^\prime) \cap Y \subseteq \interior(K_i^\prime \cap Y)$ and $\interior(K_1^\prime) \cap \interior(K_2^\prime) \subseteq \interior(K_1^\prime \cap K_2^\prime)$ (verify this.)		
	\end{proof}

@@

	\begin{proof}
		Let $K$ and $M$ be compact subsets of $X$ with $\widetilde K = K \cap Y \subset \interior M$. For every $y \in \widetilde K$, considering the open neighborhood $\interior M$, let $U_y$ be the open set such that $\im r_{U_y \cap Y, M}$ is finite. Cover $\widetilde K$ with a finite number of such open sets $\{v_1, \dots v_n\}$. The beginning of the Mayer-Vietoris sequence gives us
		\begin{equation*}
		\begin{tikzcd}
		\bigoplus_i^n H_0(\widetilde{U_i}) \arrow[r] \arrow[d, "0"] & H_0(\widetilde{K}) \arrow[d] \arrow[r] & 0 \\
		\bigoplus_i^n H_0(M) \arrow[r] & H_0(M). &
		\end{tikzcd}
		\end{equation*}
	\end{proof}
\end{document}

>>>>

	\paragraph{Terminology} A \textit{neighborhood} of a point is a set containing an open neighborhood of it.

	\begin{theorem}
		Let $X$ be locally compact and Hausdorff and $Y \subseteq X$ compact.
		\begin{itemize}
			\item[$(r^n)$] If $K$ and $M$ are compact subsets of $X$ with $\widetilde K = K \cap Y \subset \interior M$, then $\im r^n_{\widetilde K, M}$ is finite.
			\item[$(r^n_\bullet)$] If $V$ is an open neighborhood in $X$ of $y \in Y$ there exist another such neighborhood $U \subseteq V$ such that $\im r^n_{U \cap Y, V}$ is finite.
		\end{itemize}
		Then, $(r^{n-1})$ together with $(r^n_\bullet)$ imply $(r^n)$.
	\end{theorem}

	\begin{proof}
		Let $M$ be fixed and let $\sigma$ be the set of compact subsets $K$ with $K \cap Y \subseteq \interior M$ such that $K$ has a neighborhood $U_K$ such that $\im r^n_{U_K \cap Y, M}$ is finite.

		Recall the following fact:
		$(\ast)$ A space $S$ if locally compact and Hausdorff if and only if for every point $p$ of $S$, any neighborhood of $p$ contains a compact neighborhood of $p$.

		For $i \in \{1, 2\}$ consider $K_i \in \sigma$ and let $K_i^\prime$ and $K_i^\dprime$ be compact neighborhoods of $K_i$ such that
		\begin{equation*}
		K_i \subseteq K_i^\dprime \subseteq \interior K_i^\prime \subseteq K_i^\prime \subseteq U_i,
		\end{equation*}
		where $\im r^n_{U_i \cap Y, M}$ is finite. 
		We can construct such compact neighborhoods using $(\ast)$ as follows:

		Consider for each $p \in K_i$ a compact neighborhood $K^\prime_i(p) \subseteq U_i$ and let $K_i^\dprime(p) \subseteq \interior K_i^\prime(p)$ be another compact neighborhood of $p$. The collection of open sets $\interior K_i^\dprime(p)$ covers the compact $K_i$, and a finite union of the corresponding compact neighborhoods form the desired $K_i^\prime, K_i^\dprime$.

		Furthermore, we have $K^\dprime_1 \cap K^\dprime_2 \cap Y \subseteq \interior(K_1^\prime \cap K_2^\prime \cap Y)$. To see this (if not immediately), take $p \in K^\dprime_1 \cap K^\dprime_2 \cap Y$, since by assumption there exist open sets $V_i$ in $X$ such that $p \in V_i \cap K_i^\prime$. Letting $V = V_1 \cap V_2$ we have $p \in V \cap (K^\prime_1 \cap K^\prime_2)$ and, since $p \in Y$, $p \in V \cap (K^\prime_1 \cap K^\prime_2 \cap Y)$ implying the claim.

		Using $\widetilde{K}$ to denote $K \cap Y$ we have the commutative diagram
		\begin{equation*}
		\begin{tikzcd}
		& \arrow[r] \arrow[d] H^n(M) & H^n(M) \oplus H^n(M) \arrow[d] \\
		H^{n-1}(\widetilde K_1^\prime \cap \widetilde K_2^\prime) \arrow[r] \arrow[d] & 
		H^{n}(\widetilde K_1^\prime \cup \widetilde K_2^\prime) \arrow[r] \arrow[d] &
		H^{n}(\widetilde K_1^\prime) \oplus H^n(\widetilde K_2^\prime) \\
		H^{n-1}(\widetilde K_1^\dprime \cap \widetilde K_2^\dprime) \arrow[r] & 
		H^{n}(\widetilde K_1^\dprime \cup \widetilde K_2^\dprime). &
		\end{tikzcd}
		\end{equation*}
		The upper right square has finite image because $\im r^n_{\widetilde K^\prime_i, M}$ is finite. The bottom left square has a finite image using property $(r^{n-1})$. From standard homological algebra using that the middle row is exact we conclude that $K_1 \cup K_2 \in \sigma$.

		Notice that because of $(r_\bullet^n)$ and $(\ast)$, the collection $\sigma$ contains a compact neighborhood of each $y \in Y$.

		Let $K$ compact such that $\widetilde K = K \cap Y \subset \interior M$. We can cover $\widetilde{K}$ with finitely many sets in $\sigma$ and conclude that $K$ is itself in $\sigma$.
	\end{proof}
\end{document}

@@

\begin{proof}
	Let $K$ and $M$ be compact subsets of $X$ with $\widetilde K = K \cap Y \subset \interior M$. For every $y \in \widetilde K$, considering the open neighborhood $\interior M$, let $U_y$ be the open set such that $\im r_{U_y \cap Y, M}$ is finite. Cover $\widetilde K$ with a finite number of such open sets $\{v_1, \dots v_n\}$. Since
	\begin{equation*}
	\begin{tikzcd}
	\bigoplus_i^n H_0(\widetilde{U_i}) \arrow[r] \arrow[d, "0"] & H_0(\widetilde{K}) \arrow[d] \arrow[r] & 0 \\
	\bigoplus_i^n H_0(M) \arrow[r] & H_0(M) &
	\end{tikzcd}
	\end{equation*}
	commutes, we have the desired conclusion.
	(Verify the universal coefficients theorem here recalling that $H_0$ is always free.)
\end{proof}
